\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{tcolorbox}
\tcbuselibrary{skins, breakable}
\usepackage{sectsty}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fancyhdr}

% ---------- Colors ----------
\definecolor{TCTitle}{HTML}{F59E0B} % Amber
\definecolor{TCHeader}{HTML}{111827} % Slate-900
\definecolor{TCAux}{HTML}{6B7280} % Slate-500
\definecolor{TCAdd}{HTML}{22C55E} % Green-500
\definecolor{TCUpd}{HTML}{3B82F6} % Blue-500
\definecolor{TCRem}{HTML}{EF4444} % Red-500
\definecolor{TCBg}{HTML}{F8FAFC}  % Slate-50

% ---------- Hyperref ----------
\hypersetup{
  colorlinks=true,
  linkcolor=TCTitle,
  urlcolor=TCUpd,
  citecolor=TCUpd
}

% ---------- Section styling ----------
\sectionfont{\color{TCTitle}}
\subsectionfont{\color{TCHeader}}
\subsubsectionfont{\color{TCHeader}}

% ---------- Header / Footer ----------
\pagestyle{fancy}
\fancyhf{}
\lhead{\textbf{Seasonal Update Notes}}
\rhead{\textcolor{TCAux}{Summer 2025}}
\cfoot{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\headrule}{\hbox to\headwidth{%
  \color{TCTitle}\leaders\hrule height \headrulewidth\hfill
}}

% ---------- Tag badges ----------
\newcommand{\Tag}[2]{%
  \tcbox[
    on line,
    colback=#2!12,
    colframe=#2,
    coltext=#2!10!black,
    boxrule=0.5pt,
    top=0.5pt,
    bottom=0.5pt,
    left=4pt,
    right=4pt,
    rounded corners,
    nobeforeafter
  ]{\scriptsize\bfseries #1}%
}
\newcommand{\ADD}{\Tag{ADD}{TCAdd}}
\newcommand{\UPD}{\Tag{UPDATE}{TCUpd}}
\newcommand{\REM}{\Tag{REMOVE}{TCRem}}

% ---------- Section header helper ----------
\newcommand{\Section}[1]{%
  \vspace{0.5em}
  \begin{tcolorbox}[
    colback=TCBg,
    colframe=TCTitle,
    boxrule=0.8pt,
    left=8pt,
    right=8pt,
    top=6pt,
    bottom=6pt,
    enhanced,
    sharp corners
  ]
    \textbf{\large #1}
  \end{tcolorbox}
}

% ---------- Lists spacing ----------
\setlist[itemize]{left=1.2em, topsep=3pt, itemsep=4pt}
\setlist[enumerate]{left=1.5em, topsep=3pt, itemsep=4pt}
\setlength{\parskip}{4pt}
\setlength{\parindent}{0pt}

% ---------- Document ----------
\title{\textbf{Vault Heist} --- Seasonal Update Notes}
\author{}
\date{Summer 2025}

\begin{document}
\maketitle

\begin{tcolorbox}[
  colback=TCUpd!6,
  colframe=TCUpd,
  boxrule=0.8pt,
  enhanced,
  breakable,
  sharp corners
]
\textbf{The mercs just hit the vault and came back loaded with fresh content,
and plenty of goodies to go around!}
\end{tcolorbox}

\textbf{Legend:} \ADD\quad \UPD\quad \REM

\Section{Seasonal Battlepasses}

\begin{itemize}
  \item \UPD\ You ever wish there was more to do outside of pushing carts,
        standing on control points, and spending your precious time defending?
        With this update, we’re unveiling a brand new seasonal pass system
        alongside a new premium currency, Intel!
  \item \UPD\ The seasonal battlepasses are a new means to earn items and our
        newest currency. Each tier holds a reward that requires XP to be
        claimed. You automatically progress onto the next tier and can claim
        your items whenever.
\end{itemize}

\Section{New Contract System}

\begin{itemize}
  \item \UPD\ Contracts have been completely overhauled!
  \item \UPD\ Contracts are split into three different sections: Daily, Weekly,
        and Seasonal.
  \begin{itemize}
    \item \UPD\ \textbf{Daily} contracts are contracts you receive every day,
          and are generally easy objectives that do not take long to complete.
          These contracts only reward you with funds.
    \item \UPD\ \textbf{Weekly} contracts are contracts received every week,
          and these contracts are a little more difficult than daily contracts.
          These contracts reward you with XP for your seasonal pass.
    \item \UPD\ \textbf{Seasonal} contracts are contracts received every
          season, and these contracts are the hardest of them all. They give
          huge boosts of XP for your seasonal pass.
  \end{itemize}
\end{itemize}

\Section{Intel Store}

\begin{itemize}
  \item \UPD\ Just because you weren’t there, doesn’t mean you miss out! The
        Intel store has finally opened and with it, comes a whole list of
        items you’ve probably been dying to get your hands on! Spend your
        Intel here but be warned, Intel is \emph{much} harder to obtain than
        Funds.
  \item \UPD\ The archived section of this store contains items you might’ve
        not gotten, whether it be reskins or cosmetics. Any item purchased
        from here will be in Unique quality, not be sellable/giftable, and
        will be marked with a ``Purchased from Fitten Co.’s Archived Store''
        tag.
\end{itemize}

\Section{UGC Section}

\begin{itemize}
  \item \UPD\ Ever wanted to show your support for RED or GRN? Maybe even have
        yourself a Dorcus Cap or a Typical Colors Cap on the go? We’ve now
        expanded our gamepasses section to include new UGC that provide
        in-game rewards! All of our UGC will only be purchasable in-game, and
        will reward you upon purchase. More UGC will come soon, so keep an eye
        out for any more UGC we release!
  \item \UPD\ The Dorcus Cap UGC will reward you with the Beetle Brooch, the
        RED, GRN, and Typical Colors caps will reward you with the Team Cap.
        Every item you are rewarded in-game will be in Genuine quality.
\end{itemize}

\Section{Intel Store}

\begin{itemize}
  \item \UPD\ Just because you weren’t there, doesn’t mean you miss out! The
        Intel store has finally opened and with it, comes a whole list of
        items you’ve probably been dying to get your hands on! Spend your
        Intel here but be warned, Intel is \emph{much} harder to obtain than
        Funds.
  \item \UPD\ The archived section of this store contains items you might’ve
        not gotten, whether it be reskins or cosmetics. Any item purchased
        from here will be in Unique quality, not be sellable/giftable, and
        will be marked with a ``Purchased from Fitten Co.’s Archived Store''
        tag.
\end{itemize}

\Section{UGC Section}

\begin{itemize}
  \item \UPD\ Ever wanted to show your support for RED or GRN? Maybe even have
        yourself a Dorcus Cap or a Typical Colors Cap on the go? We’ve now
        expanded our gamepasses section to include new UGC that provide
        in-game rewards! All of our UGC will only be purchasable in-game, and
        will reward you upon purchase. More UGC will come soon, so keep an eye
        out for any more UGC we release!
  \item \UPD\ The Dorcus Cap UGC will reward you with the Beetle Brooch, the
        RED, GRN, and Typical Colors caps will reward you with the Team Cap.
        Every item you are rewarded in-game will be in Genuine quality.
\end{itemize}

\Section{Maps}

\begin{itemize}
  \item \ADD\ Financial (Attack/Defense)
  \item \ADD\ Deadfall Ridge (Attack/Defense)
  \item \ADD\ Pervade (Payload)
  \item \ADD\ Waterbog (TDM) \\
        \textit{by \texttt{<@837759119338373170>} and
        \texttt{<@548520395964153858>}}
  \item \ADD\ Highlands (3CP) \\
        \textit{by \texttt{<@949424873124540427>}}
  \item \ADD\ Doublefort Table (VS. Bosses) \\
        \textit{by \texttt{<@591990119737720842>} and
        \texttt{<@1004233181282697216>}}
  \item \UPD\ Cliffhanger (Attack/Defense)
  \begin{itemize}
    \item \UPD\ Given a new artpass by \texttt{<@799349935736225804>}.
  \end{itemize}
\end{itemize}

\Section{Cosmetics}

\subsection*{Summer 2025 Brown Cosmetic Cooler}
\begin{itemize}
  \item \ADD\ Detonator’s Do
  \item \ADD\ Field Ready
  \item \ADD\ First Impression
  \item \ADD\ Infiltrator
  \item \ADD\ Marketeer Munch
  \item \ADD\ Medibun
  \item \ADD\ Off The Case
  \item \ADD\ On The Case
  \item \ADD\ Senza Vista
  \item \ADD\ Unpaid Time Off
  \item \ADD\ Vogue Vagrant
  \item \ADD\ Warranty Void
\end{itemize}

\subsection*{New Seasonal Battlepass Cosmetics}
\begin{itemize}
  \item \ADD\ Dollar Maker
  \item \ADD\ Happy Hare
  \item \ADD\ Designated Runner
  \item \ADD\ Safe Cracker
  \item \ADD\ Raid Ready
  \item \ADD\ Faux Fawkes
  \item \ADD\ Sector Protector
  \item \ADD\ Extra Prep
  \item \ADD\ Floor Plans
  \item \ADD\ Back Up
  \item \ADD\ Damage Control
  \item \ADD\ Ladra
\end{itemize}

\subsection*{New Community Created Shop Cosmetics}
\begin{itemize}
  \item \ADD\ The Eggsecutive by \texttt{<@1260790618154860636>} and
        \texttt{<@669231862224257084>}
  \item \ADD\ The Law by \texttt{<@595453896185479175>}
  \item \ADD\ Night Watcher by \texttt{<@583784290295349280>}
  \item \ADD\ The Paper Craft by \texttt{<@577258333224960001>}
  \item \ADD\ Rangini Rango by \texttt{<@711106274514960394>}
  \item \ADD\ Rugged Looks by \texttt{<@825907488968015903>}
\end{itemize}

\subsection*{Cosmetic Remodels}
\begin{itemize}
  \item \ADD\ Dead Eye
  \item \ADD\ Outlaw Hunter
  \item \ADD\ Squared Shades
  \item \ADD\ Batter’s Helmet
  \item \ADD\ Hard News
  \item \ADD\ Beetle Brooch
\end{itemize}

\Section{Unusuals}

\begin{itemize}
  \item \ADD\ Criminal Network (Seasonal Track)
  \item \ADD\ Decrypted (Intel Shop)
  \item \ADD\ Disruptive Wave (Intel Shop)
  \item \ADD\ Robbed Riches (Intel Shop)
  \item \ADD\ Secured (Intel Shop)
  \item \ADD\ Thermite Charge (Funds Shop)
  \item \ADD\ Digital Invader (Funds Shop) by
        \texttt{<@97726309233972029>} and
        \texttt{<@1357501154053066794>}
  \item \ADD\ Summer Dew (Funds Shop) by
        \texttt{<@1019267003669807154>}
\end{itemize}

\Section{Taunts}

\begin{itemize}
  \item \ADD\ En Garde (Funds Shop)
  \item \ADD\ Termination Sequence (Funds Shop)
  \item \ADD\ The Comic Relief (Funds Shop)
  \item \ADD\ Blood Money (Seasonal Track)
  \item \ADD\ Stolen Valor (Seasonal Track)
\end{itemize}

\Section{Weapons}

\begin{itemize}
  \item \ADD\ Sumatran Claw (Seasonal Track)
  \begin{itemize}
    \item \UPD\ Reskin of the Knife
  \end{itemize}
  \item \ADD\ Counter Service (Seasonal Track)
  \begin{itemize}
    \item \UPD\ Reskin of the MAC-10
  \end{itemize}
\end{itemize}

\subsection*{Weapon Changes}

\begin{itemize}
  \item \ADD\ Aerial Bomber --- Redesigned into the \textit{Stellar Carpet}
  \item \ADD\ Loose Cannon --- Redesigned into the \textit{BlunderBrass}
  \item \ADD\ Blackbox --- Redesigned into \textit{The Great Unifier}
  \item \ADD\ Bushman’s Bushcutter --- Redesigned into the \textit{Gustabe}
  \item \ADD\ Bloody Bracer --- Redesigned into the \textit{Bloody Blossom}
  \begin{itemize}
    \item \ADD\ Bloody Blossom includes 2 different styles.
  \end{itemize}
  \item \UPD\ Stickybomb Launcher --- Resized to be smaller.
  \item \ADD\ Rocket Launchers, Poacher’s Pride, Boonie Blaster, Katana,
        Coils, Machetes, Saws, and Fists --- New viewmodel animations.
  \item \ADD\ Shotguns, Pistols, Boonie Blaster, Lever Shotguns, Grenade
        Launchers, SMGs, Stickybomb Launcher, Poacher’s Pride, and DB
        Shotguns --- New worldmodel animations.
  \item \UPD\ Homewrecker, Cozy Camper, and The Avenger --- Renamed to
        \textit{Hotwire}, \textit{Hermits’ Haversack}, and \textit{Avengeance}
        respectively.
\end{itemize}

\subsection*{Balancing Changes}

\begin{itemize}
  \item \UPD\ Miniguns
  \begin{itemize}
    \item \ADD\ Damage penalty upon initial rev increased from -65\% to
          -50\%.
    \item \ADD\ Damage and accuracy rampup over time is much faster.
  \end{itemize}
  \item \UPD\ Tide Turner
  \begin{itemize}
    \item \REM\ No longer grants resistances on wearer.
  \end{itemize}
  \item \UPD\ Wraith
  \begin{itemize}
    \item \ADD\ Weapon no longer holsters 25\% slower.
    \item \ADD\ Disguising no longer consumes a full cloak meter.
    \item \REM\ All backstabs now mini-crit.
  \end{itemize}
  \item \UPD\ Afterimage
  \begin{itemize}
    \item \REM\ Speed boost while cloaked reduced from 1.3x to a 1.2x boost.
    \item \UPD\ Trail now tracks the player.
  \end{itemize}
  \item \UPD\ Disguise Kit
  \begin{itemize}
    \item \ADD\ Can now disguise as classes even if a team does not have a
          player of that class.
  \end{itemize}
  \item \UPD\ Noisy Cricket
  \begin{itemize}
    \item \ADD\ Amount of damage that's returned as metal increased from
          70\% to 100\%.
  \end{itemize}
  \item \UPD\ Disciplinary Action
  \begin{itemize}
    \item \ADD\ Grants a speed boost on kill.
  \end{itemize}
  \item \UPD\ Knockback
  \begin{itemize}
    \item \ADD\ At lower damages, knockback has been reduced.
  \end{itemize}
  \item \UPD\ Marked for Death
  \begin{itemize}
    \item \ADD\ Icon no longer shows through walls.
  \end{itemize}
  \item \UPD\ Brute Primaries, Conventional, Tenacious Turkey, Syringe
        Crossbows, Supersaw, Sandman, Ambassador, Mischievous Machete, Urban
        Upriser, Your Eternal Reward, Quick Draw, and Liberty Launcher
  \begin{itemize}
    \item \UPD\ Updated visible weapon stats.
  \end{itemize}
\end{itemize}

\subsection*{Experimental Changes}

\begin{itemize}
  \item \UPD\ Barrett’s Privateer
  \begin{itemize}
    \item \ADD\ No longer has a draw speed penalty.
    \item \REM\ No longer has an increased healing range.
    \item \REM\ Damage resistance reduced from 50\% to 30\%.
    \item \REM\ Pole healing reduced from 75 HPS to 35 HPS.
    \item \REM\ Damage resistance’s length after leaving the pole radius
          reduced from 10 seconds to 1.5 seconds.
    \item \REM\ -33\% SuperCharge duration.
    \item \REM\ Allies within pole radius receive -75\% SuperCharge effect
          while contesting an objective.
    \item \UPD\ Updated VFX for the pole.
  \end{itemize}
  \item \UPD\ World Champion
  \begin{itemize}
    \item \UPD\ Made Brute’s pick up status more apparent with VFX, proper
          indicators, and prompts.
    \item \UPD\ Players being carried can press alt-fire to stop being
          carried.
    \item \UPD\ Brutes carrying someone can now press alt-fire to drop carried
          player.
    \item \UPD\ Weapon’s pick up, throw, and carry now all have animations.
  \end{itemize}
\end{itemize}

\Section{Bug Fixes and Miscellaneous Changes}

\begin{itemize}
  \item \ADD\ Added new font settings.
  \item \ADD\ Added drop camera VIP option.
  \item \ADD\ Remade Strangifier and Unusualifier icons.
  \item \ADD\ Added new theme for Unfortunate Son.
  \item \ADD\ Added right handed gestures for certain weapons such as Sniper
        Rifles and Lever Shotguns.
  \item \ADD\ Added additional countdown GUI when rounds are starting.
  \item \UPD\ Increased class limits from 2 to 3.
  \item \UPD\ Mobile and console players under level 40 and 20 respectively
        get teleported to their own servers.
  \item \UPD\ Added loading bar to shop.
  \item \UPD\ Redid the gamepass section into
        \emph{[text truncated in source]}.
  \item \UPD\ Fixed a lot of achievements being impossible or bugged.
  \item \UPD\ Fixed notification for achievement or achievement progress not
        showing up.
  \item \UPD\ Fixed a bug where Self-Made and Community weapons’ sparkles
        didn’t appear in the viewmodel.
  \item \UPD\ Fixed detection of gamepass purchase on server.
  \item \UPD\ Improved feedback on cloaking and being on fire.
  \item \UPD\ Converted existing Unique/Strange Frying Pans, Three Rune
        Blades, and Handymans into Vintage.
  \item \UPD\ Fixed Jack-O Roger using older viewmodel animations and missing
        visible stats.
  \item \UPD\ Updated explosion particles and added setting for transparency.
  \item \UPD\ Added a setting to disable certain ragdoll kill effects.
  \item \UPD\ Fixed an issue where you couldn’t delete unsellable items.
  \item \UPD\ Fixed a bug where closing the taunt menu would make you switch
        to your previous weapon.
  \item \UPD\ Shields no longer delete parts of clothing that’re of the same
        attachment.
  \item \UPD\ Gametypes are now their own server page on the browser.
  \item \UPD\ Rewrote some weapon descriptions.
  \item \UPD\ Fixed some weapons missing sounds.
  \item \UPD\ Fixed Spare Hand not having a projectile model.
  \item \UPD\ Fixed a bug involving buildings not taking stomp damage.
  \item \UPD\ Distance to display subtitles for voicelines in chat lowered to
        30 studs for non-teammates, 60 for teammates from 40 \& 80
        respectively.
  \item \UPD\ Adjusted Nuts and Bolts to make it spawn earlier.
  \item \UPD\ Afterimage particles properly render on all graphics settings.
\end{itemize}

\end{document}